Amicus Word Count

### 2021-11-10 data-cleaning/01-shorten-amicus-text.Rmd
update file saves, list of app/fn briefs

```{r}
amicus <- amicus %>%
  mutate(appendix = str_count(txt_full, "appendix"),
         footnotes = str_count(txt_full, "footnote"))

amicus %>% select(case, brief, id, appendix, footnotes) %>% 
  filter(appendix==0 & footnotes==0)
```

@@

```{r}
amicus %>% colnames
```

```{r}
box_write(amicus,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

```{r}
amicus_ends <- amicus %>%
  mutate(appendix = str_count(txt_short, "appendix"),
         appendices = str_count(txt_short, "appendices"),
         footnotes = str_count(txt_short, "footnotes"))

amicus_ends <- amicus_ends %>% select(case, brief, id, appendix, footnotes)

#box_write(amicus_ends,
#          file_name = "amicus appendix and footnotes counts.csv",
#          dir_id = 145990409196)
```

@@

```{r}
amicus <- amicus %>% select(-txt_full)
amicus %>% colnames
```

```{r}
box_write(amicus,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = 145990409196)
```
